---
title: "Facebook_EDA"
author:"Yuqing Yang|Zitong Feng"
output: pdf_document
date: "2023-09-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(tidyverse)
```

### Set Working Directory

First, set the working directory to the location where your data is stored on your computer. Uncomment and modify the `setwd` line as needed.

```{r}
setwd("~/Desktop/MA575/GroupProject")
```

## Data Import and Exploration

### Read Data

Let's start by reading the data from a CSV file using a semicolon as the delimiter.

```{r}
# Read data from a CSV file using semicolon as delimiter
data <- read.csv("./data/dataset_Facebook.csv", header=TRUE, as.is=TRUE, sep=';')
```

### Check Missing Values

```{r}
# Summary of each column
summary(data)

```
summary:
- NA values in variable "Paid","Like","share"
- In total 500 observations and 19 variables including categorical variables

## Data Visualization

### Scatterplot

Let's create a scatterplot of Ground CO.

```{r}
# Scatterplot of Ground CO
plot(GroundCO)
```