---
title: "Facebook_EDA"
output: pdf_document
date: "2023-09-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(tidyverse)
library(ggplot2)
library(GGally)
```

### Set Working Directory

First, set the working directory to the location where your data is stored on your computer. Uncomment and modify the `setwd` line as needed.

```{r}
#setwd("~/Desktop/MA575/GroupProject/facebook-metrics")
```

## Data Import and Exploration

### Read Data

Let's start by reading the data from a CSV file using a semicolon as the delimiter.

```{r}
# Read data from a CSV file using semicolon as delimiter
fc_data <- read.csv("dataset_Facebook.csv", header=TRUE, as.is=TRUE, sep=';')
```

### Check Missing Values

```{r}
# Summary of each column
summary(fc_data)
```

-   NA values in variable "Paid","Like","share".
-   In total 500 observations and 19 variables including categorical variables.
-   Original dataset is clean enought for later analysis.

## Data Visualization

### Scatterplot Matrix using ggplot2

```{r }
temp_data<-fc_data %>% select(starts_with("Lifetime"))

pair1<- ggpairs(temp_data,
        lower=list(continuous=wrap("density", alpha=0.5), combo="box"),
        upper=list(continuous=wrap("points", alpha=0.3, size=0.1)), labeller = label_wrap_gen(5, multi_line = TRUE)) 
 pair1<- pair1 + theme(axis.text.x = element_text(angle = 40, hjust = 1, size = 7), axis.text.y = element_text(vjust = 1, size = 7))
 pair1

```

```{r2}
pair2<- ggpairs(temp_data,
        lower=list(continuous=wrap("points", alpha=0.3, size=0.1)),
        upper=list(continuous=wrap("cor", size=4)))
pair2 + theme(axis.text.x = element_text(angle = 40, hjust = 1, size = 7), axis.text.y = element_text(vjust = 1, size = 7))
pair2
```

-   High correlation between Lifetime.Post.Consumptions and Lifetime.Engaged.Users
-   Lifetime.Post.Consumptions: The number of clicks anywhere in a post.
-   Lifetime.Engaged.Users: The number of people who clicked anywhere in a post (unique users).

### Find Outliers

- not required so far for deliverable 2

### Scatterplot

```{r scatterplot}
plot(fc_data$Lifetime.Post.Consumptions,fc_data$Lifetime.Engaged.Users,
     xlab="Lifetime Post Consumptions",
     ylab="Lifetime Post Engaged User Count",
     pch=19, cex=0.2)+
abline(lsfit(x=fc_data$Lifetime.Post.Consumptions,y=fc_data$Lifetime.Engaged.Users), col="blue")
```
